Software Citation Principles

### 2016-04-05 sc-principles/software-citation-principles.tex
update to importance principle as per Martin Fenner in issue 99

\begin{enumerate}
\item \textbf{Importance}: \label{principle:importance} Software should be
considered a legitimate and citable product of research. Software citations should
be accorded the same importance in the scholarly record as citations of other
research products, such as publications and data; they should be part of the
standard reference list for a research product and should not be omitted or separated.
Software should be cited on the same basis as any other research products such as
papers or books, that is, authors should cite the appropriate set of software
products just as they cite the appropriate set of papers.

>>>>

\begin{enumerate}
\item \textbf{Importance}: \label{principle:importance} Software should be
considered a legitimate and citable product of research. Software citations should
be accorded the same importance in the scholarly record as citations of other
research products, such as publications and data; they should be included in the
metadata of the citing work, for example in the reference list of a journal article,
and should not be omitted or separated.
Software should be cited on the same basis as any other research products such as
papers or books, that is, authors should cite the appropriate set of software
products just as they cite the appropriate set of papers.

software that was cited should be included in the metadata of the citing work, for example in the reference list of a journal article
